Storm surge modelling in the Strait of Georgia

### 2014-11-20 RoughWork/manuscript.tex
Adjusted new figure captions

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 14.0           &  3.45                & 3.55                 &   0.012    & 0.995  &  6.1           &  0.313                 & 0.331                  &  0.237     & 0.913 \\
Victoria       &  9.9           &  2.25                & 2.24                 &   0.023    & 0.989  &  4.8           &  0.323                 & 0.293                  &  0.245     & 0.899 \\
Patricia Bay   & 11.2           &  2.50                & 2.65                 &   0.020    & 0.997  &  6.0           &  0.277                 & 0.290                  &  0.272     & 0.901 \\
Campbell River & 13.5           &  3.22                & 3.27                 &   0.019    & 0.991  &  4.9           &  0.326                 & 0.314                  &  0.217     & 0.924 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Nov 2009 hindcast.}
\label{tab:nov2009stat} 
\end{table}
%Fix label for CGRF: Atmospheric model

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_surge.pdf}
\caption{Comparison modelled residuals using a low resolution and high resolution atmospheric product during the Dec 2012 storm surge simulation. }
\label{fig:dec2012_surge}
\end{figure}
%Add in observations?

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson and Sandheads.}
\label{fig:dec2013_weather}
\end{figure}

>>>>

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 14.0           &  3.45                & 3.55                 &   0.012    & 0.995  &  6.1           &  0.313                 & 0.331                  &  0.237     & 0.913 \\
Victoria       &  9.9           &  2.25                & 2.24                 &   0.023    & 0.989  &  4.8           &  0.323                 & 0.293                  &  0.245     & 0.899 \\
Patricia Bay   & 11.2           &  2.50                & 2.65                 &   0.020    & 0.997  &  6.0           &  0.277                 & 0.290                  &  0.272     & 0.901 \\
Campbell River & 13.5           &  3.22                & 3.27                 &   0.019    & 0.991  &  4.9           &  0.326                 & 0.314                  &  0.217     & 0.924 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Nov 2009 hindcast.}
\label{tab:nov2009stat} 
\end{table}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_surge.pdf}
\caption{Comparison observed (solid black) and modelled residuals for the Dec 2012 storm surge simulation. Modelled residuals from two simulations using a low resolution (dashed) and high resolution (gray) atmospheric product are shown. }
\label{fig:dec2012_surge}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson and Sandheads.}
\label{fig:dec2013_weather}
\end{figure}
